### 2017-07-31 doc/manual/version3/inputParameters.tex
Edited input variables to logicals. Made associated edits to manual and writehdf5 including a writeHDF5Booleans procedure

{\ttfamily RHSMode} = 3: Solve for the 2$\times$2 monoenergetic transport coefficients. When this option is chosen, \Nx~is set to 1 and only 1 species is used.
}

@@

>>>>

{\ttfamily RHSMode} = 3: Solve for the 2$\times$2 monoenergetic transport coefficients. When this option is chosen, \Nx~is set to 1 and only 1 species is used. \\

{\ttfamily RHSMode} = 4: Solve the adjoint equation at constant $E_r$. This must be used with {\ttfamily geometryScheme == 5}, stellarator symmetric geometry, {\ttfamily includePhi1 = .false.}, {\ttfamily EParallelHat == 0}, {\ttfamily useDKESExBDrift == .false.}, {\ttfamily magneticDriftScheme == 0}, {\ttfamily includeXDotTerm == .true.}, {\ttfamily constraintScheme == 1}, and {\ttfamily collisionOperator == 0}. \\

{\ttfamily RHSMode} = 5: Solve the adjoint equation at the ambipolar $E_r$. The same input parameters must be used as those detailed for {\ttfamily RHSMode == 4}. 
}

@@

\section{The \texttt{sensitivityOptions} namelist}

\param{adjointBootstrapOption}
{Boolean}
{{\ttfamily .false. }}
{When {\ttfamily RHSMode == 4} or {\ttfamily RHSMode == 5}. }
{If this parameter is {\ttfamily .true.}, the sensitivity of the bootstrap current will be computed.}

\param{adjointRadialCurrentOption}
{Boolean}
{{\ttfamily .false. }}
{When {\ttfamily RHSMode == 4} or {\ttfamily RHSMode == 5}. }
{If this parameter is {\ttfamily .true.}, the sensitivity of the radial current will be computed.}

\param{adjointTotalHeatFluxOption}
{Boolean}
{{\ttfamily .false. }}
{When {\ttfamily RHSMode == 4} or {\ttfamily RHSMode == 5}. }
{If this parameter is {\ttfamily .true.}, the sensitivity of the species-summed heat flux will be computed.}

\param{adjointHeatFluxOption}
{1D array of booleans}
{0}
{When {\ttfamily RHSMode == 4} or {\ttfamily RHSMode == 5}} 
{This array is of the same length of {\ttfamily nHats} and other species parameters. If parameter is {\ttfamily .true.}, the sensitivity of the heat flux will be computed for this species.}

\param{adjointParticleFluxOption}
{1D array of booleans}
{0}
{When {\ttfamily RHSMode == 4} or {\ttfamily RHSMode == 5}}
{This array is of the same length of {\ttfamily nHats} and other species parameters. If parameter is {\ttfamily .true.}, the sensitivity of the particle flux will be computed for this species.}
